%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Entrepreneurship}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {JobsChange.com -- AI Career Acceleration Platform} % Organization
    {India} % Location
    {2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an AI-powered career platform that tailors resumes to job descriptions, generates cover letters, and provides mock interview preparation using OpenAI GPT-5.}
        \item {Engineered full-stack application with Next.js 15, React 19, TypeScript, and Firebase, featuring real-time AI resume analysis and ATS compatibility scoring.}
        \item {Developed Chrome extension supporting 50+ ATS platforms (Workday, Greenhouse, Lever, Taleo) for one-click job application autofill.}
        \item {Implemented AI mock interview system with voice-based Q\&A using Vapi, providing real-time feedback and performance scoring.}
        \item {Built integrated coding practice module with AI-generated problems, automated test case validation, and difficulty progression.}
        \item {Designed credit-based monetization system with Stripe payment integration and tiered subscription plans.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder} % Job title
    {MakeDemos.com -- Professional Screen Recording \& Demo Software} % Organization
    {India} % Location
    {2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a desktop screen recording application for creating polished product demos with auto-zoom, 50+ visual effects, and 4K export capabilities.}
        \item {Engineered cross-platform desktop app using Electron 30, React 18, and PixiJS 8 with GPU-accelerated rendering pipeline via Web Codecs API.}
        \item {Implemented intelligent auto-zoom that tracks cursor movements and click events, automatically framing key actions during recordings.}
        \item {Developed real-time video effects engine with PixiJS shaders supporting transitions, annotations, blur, and spotlight effects on timeline.}
        \item {Built multi-track timeline editor supporting screen, camera, and audio tracks with frame-accurate trimming and export.}
        \item {Designed state management architecture using Zustand for real-time recording controls and Firebase for user authentication and licensing.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
