%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT (Portfolio version - key highlights only)
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
    {Lead Engineer - Gen AI } % Job title
    {Bosch Global Software Technologies} % Organization
    {Bangalore, India} % Location
    {Mar. 2023 - Current} % Date(s)
    {
      \begin{cvitems}
        \item {Leading a cross-functional team of 8+ engineers across Gen AI, automotive middleware, and cloud platform initiatives.}
        \item {Built HARA AI, a safety-relevant AI system for Hazard Analysis and Risk Assessment that automates ASIL classifications per ISO 26262.}
        \item {Architected BRICK, an advanced document analysis platform featuring PathRAG and MinerU for high-precision retrieval from unstructured PDFs.}
        \item {Won Bosch AWS Hackathon 2025 for "Project IQ," achieving 90\% accuracy in extracting competencies from SRS documents.}
        \item {Performed Parameter-Efficient Fine-Tuning (PEFT) on Qwen 7B+ models using QLoRA/LoRA with 4-bit quantization.}
        \item {Architected a Serverless Multi-Tenant SaaS platform using AWS CDK, reducing onboarding time by 90\%.}
        \item {Developed CAN-to-VSS protocol mapper and optimized KUKSA.val databroker in C++/Rust for low-latency signal orchestration.}
        \item {Represented Bosch at Bharat Mobility Expo 2025, showcasing Vehicle Assistant AI for SDV apps on HMI and HPCs.}
      \end{cvitems}
    }

 \cventry
    {SDE - II} % Job title
    {HashedIn by Deloitte} % Organization
    {Bangalore, India} % Location
    {Aug. 2021 - Mar. 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Built cloud-native content normalization platform for Thomson Reuters legal domain using AWS serverless architecture.}
        \item {Developed annotation component in Angular that reduced document content processing time from 7 days to 4 hours.}
        \item {Architected AWS serverless cloud infrastructure with relational and non-relational database integration.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Zapcom Solutions} % Organization
    {Bangalore, India} % Location
    {Feb. 2020 - July 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Built REST APIs using Python/Django DRF and implemented Celery-based async task processing.}
        \item {Created AWS instances for daily review extractions with NLP scoring using spaCy.}
        \item {Wrote automation test scripts in Python using Selenium, reducing manual testing effort by 35\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Intern} % Job title
    {Zapcom Solutions} % Organization
    {Bangalore, India} % Location
    {Jan. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Developed web scraping pipeline in Java (Selenium) and Python (Scrapy) to extract 1000+ reviews from 540+ client hotels.}
        \item {Built scene classification model using Places365 dataset for image recognition.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
