\cvsection{Work Experience}

\begin{cventries}

 \cventry
    {Lead Engineer - Gen AI}
    {Bosch Global Software Technologies}
    {Bangalore, India}
    {Mar. 2023 - Current}
    {
      \begin{cvitems}
        \item {Leading a cross-functional team of 8+ engineers across Gen AI, automotive middleware, and cloud platform initiatives.}
        \item {Built HARA AI for Hazard Analysis and Risk Assessment, automating ASIL classifications per ISO 26262.}
        \item {Architected BRICK, a document analysis platform with PathRAG for high-precision retrieval from unstructured PDFs.}
        \item {Won Bosch AWS Hackathon 2025 for "Project IQ," achieving 90\% accuracy extracting competencies from SRS documents.}
        \item {Performed PEFT on Qwen 7B+ models using QLoRA/LoRA with 4-bit quantization on limited hardware.}
        \item {Architected Serverless Multi-Tenant SaaS platform using AWS CDK, reducing onboarding time by 90\%.}
        \item {Developed CAN-to-VSS protocol mapper and optimized KUKSA.val databroker in C++/Rust for low-latency signal orchestration.}
      \end{cvitems}
    }

 \cventry
    {SDE - II}
    {HashedIn by Deloitte}
    {Bangalore, India}
    {Aug. 2021 - Mar. 2023}
    {
      \begin{cvitems}
        \item {Built cloud-native content normalization platform for Thomson Reuters legal domain using AWS Lambda, API Gateway, DynamoDB, and CloudFormation.}
        \item {Developed annotation component in Angular that reduced document content processing time from 7 days to 4 hours.}
        \item {Collaborated with US legal domain stakeholders for requirement gathering and defining technical user stories.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {Zapcom Solutions}
    {Bangalore, India}
    {Feb. 2020 - July 2021}
    {
      \begin{cvitems}
        \item {Built REST APIs using Python/Django DRF with Celery async processing and NLP scoring using spaCy.}
        \item {Built Content Management service interface handling 1000+ client devices in WSO2.}
        \item {Wrote automation test scripts in Python using Selenium, reducing manual testing effort by 35\%.}
      \end{cvitems}
    }

  \cventry
    {Full Stack Intern}
    {Zapcom Solutions}
    {Bangalore, India}
    {Jan. 2019 - Jan. 2020}
    {}

\end{cventries}
